---
title: README
author: Zhuoya Zhao
date: today
date-format: long
format: 
  html: 
    self-contained: true
    df-print: tibble
editor_options: 
  chunk_output_type: console
execute: 
  warning: false
  message: false
---

## Get libs

```{r, setup}
pacman::p_load(tidyverse, targets)
```

## Clean the dataset
Load the data set; 
select columns of interest (`genres`, `average_rating`, `christmas`); 
remove rows with all or some missing values; 
select rows `christmas` movies.
```{r}
tar_load(movies_clean)
head(movies_clean)
```

## Analyse the dataset
Because a movie might have multiple genres, we split them into different variable columns. Based on this, we reconstruct the dataset with two variable columns: one variable column for single genre and the other one for corresponding rating.
```{r}
tar_load(movies_analyse)
movies_analyse
```

## Calculate the average rating for each single genre and write into the table
```{r}
tar_load(movies_best_rating)
movies_best_rating
```

## Get the genre `Reality-TV` which gives the best rating for Christmas movies
```{r}
head(movies_best_rating,1)
```
